---
title: Midterm Project Report
author: Christina Becraft, Emalee Martin, Roland Berg, Sakshi Chauhan, Tyler Bryant, and You!
output: html_document
params:
  arm: Modified F75 (intervention)
---

```{r, here-i-am, include = FALSE}

here::i_am(
  "report.Rmd"
)

```

Feel free to load any packages you use in this section!!

```{r, load-packages, include = FALSE}

library(dplyr)
library(ggplot2)
library(gtsummary)

```
Cleaning data based on parameters (run this before loading cleandata.rds in your own code!!)

```{r, load-and-filter-data, include = FALSE}

# Loads initial dataset from the data/ folder
datapath <- here::here("data/f75_interim.csv")
data <- read.csv(datapath, header = TRUE)

# Filters data by arm status based on parameters (set by render R scripts)
cleandata <- data %>%
    filter(arm == params$arm)

# Saves filtered dataset as an .rds object for calling in individual .R scripts
saveRDS(
  cleandata,
  file = here::here("data/cleandata.rds")
)
```

Section 1: Christina

```{r, elements1}

```

## Days to Stabilization of Patients by Site
This section analyzes the number of days to stabilization of patients by site. 
There were `r n_distinct(cleandata$site)` sites total. Days to stabilization ranged 
from `r min(cleandata$days_stable)` to `r max(cleandata$days_stable[cleandata$days_stable != 999])`. 
`r sum(cleandata$days_stable == 999)` patients were unable to stabilize due to death, 
voluntary withdrawal, protocol violation, or other reasons.

```{r, section2_plot, echo=FALSE, warning=FALSE}
section2_plot <-readRDS(
  file = here::here("output/section2_plot.rds")
)
section2_plot
```

The number of patients by site was not equal. `r sum(cleandata$site == 'A')` patients 
were enrolled at site A, `r sum(cleandata$site == 'B')` at site B, and 
`r sum(cleandata$site == 'C')` at site C. 

```{r, section2_table, echo=FALSE, warning=FALSE}
section2_table <-readRDS(
  file = here::here("output/section2_table.rds")
)
section2_table
```

Section 3: Sakshi

```{r, elements3}

```

Section 4: Tyler

```{r, elements4}

```
