---
title: Midterm Project Report
author: Christina Becraft, Emalee Martin, Roland Berg, Sakshi Chauhan, Tyler Bryant, and You!
output: html_document
params:
  arm: Modified F75 (intervention)
---

```{r, here-i-am, include = FALSE}

here::i_am(
  "report.Rmd"
)

```

Feel free to load any packages you use in this section!!

```{r, load-packages, include = FALSE}

library(dplyr)
library(ggplot2)
library(gtsummary)
library(readr) #to read in csv
library(labelled) #to create nice labels
library(DataExplorer) #to plot missing data
library(glue) #to use parameters in caption
library(rmarkdown)

```
Cleaning data based on parameters (run this before loading cleandata.rds in your own code!!)

```{r, load-and-filter-data, include = FALSE}

library(dplyr)

# Loads initial dataset from the data/ folder
data <- read.csv("data/f75_interim.csv", header = TRUE)

# Filters data by arm status based on parameters (set by render R scripts)
cleandata <- data %>%
    filter(arm == params$arm)

# Saves filtered dataset as an .rds object for calling in individual .R scripts
saveRDS(
  cleandata,
  file = "data/cleandata.rds"
)
```

Section 1: Christina

Missing data is displayed in the plot below, and patient characteristics are summarized in Table 1. Note that the variable tracking sickle cell disease is not included in the table because it was present in none of the patients, with no missing data. Furthermore, measurements labelled as taken at discharge were taken at death or withdrawal from the study if the patient was not discharged. 

```{r missing-data, echo=FALSE, fig.height=8, fig.width=8}
missing_data_plot <- readRDS(
  file = here::here("output/missing_data_plot.rds")
)
missing_data_plot
```

```{r table-one, echo=FALSE}
table_one <- readRDS(
  file = here::here("output/table_one.rds")
)
table_one
```

## Days to Stabilization of Patients by Site
This section analyzes the number of days to stabilization of patients by site. 
There were `r n_distinct(cleandata$site)` sites total. Days to stabilization ranged 
from `r min(cleandata$days_stable)` to `r max(cleandata$days_stable[cleandata$days_stable != 999])`. 
`r sum(cleandata$days_stable == 999)` patients were unable to stabilize due to death, 
voluntary withdrawal, protocol violation, or other reasons.

```{r, section2_plot, echo=FALSE, warning=FALSE}
section2_plot <-readRDS(
  file = here::here("output/section2_plot.rds")
)
section2_plot
```

The number of patients by site was not equal. `r sum(cleandata$site == 'A')` patients 
were enrolled at site A, `r sum(cleandata$site == 'B')` at site B, and 
`r sum(cleandata$site == 'C')` at site C. 

```{r, section2_table, echo=FALSE, warning=FALSE}
section2_table <-readRDS(
  file = here::here("output/section2_table.rds")
)
section2_table
```

Section 3: Sakshi

This section summarizes key clinical outcomes and complications during admission, focusing on shock, impaired consciousness, severe pneumonia, diarrhoea, malaria, tuberculosis, HIV status, and reasons for withdrawal from therapy. We present a table of withdrawal outcomes by treatment arm and a bar plot showing the distribution of withdrawal reasons across arms.

```{r, elements3, echo=FALSE}
outcome_table <- readRDS(
  file = here::here("output/outcome_table.rds")
)
withdraw_plot <- readRDS(
  file = here::here("output/withdraw_plot.rds")
)

outcome_table
withdraw_plot
```

Section 4: Tyler

```{r, elements4}

```
